### 2016-10-20 capability-machine.tex
Added two missing lemmas (not yet proven) and some labels

@@

@@

\subsubsection{Expression Relation}
\label{subsubsection:expression-relation}
The expression relation is defined as follows:
\begin{align*}
  \stder \quad : & \quad  (\Worlds \monnefun \UPred{\Words}) \nefun \Worlds \nefun \UPred{\Words} \\%TODO: Check whether this needs to be monotone
  \stder \defeq & \lambda \stdvr \ldotp \lambda W \ldotp \{ \npair{\pc} \mid 
  \begin{aligned}[t]
    & \forall n' \leq n \ldotp\\
    & \quad \forall \npair[n']{\reg} \in \stdrr(\stdvr)(W) \ldotp \\
    & \quad \quad \forall \npair[n']{c} \in \stdkr(\stdvr)(W) \ldotp \\
    & \quad \qquad  \forall \heapSat[\hs]{n'}{W} \ldotp \\
    & \quad \qquad \quad \npair[n']{(\reg\update{r_0}{c}\update{\pcreg}{\pc},\hs)} \in \observations(W) \}
  \end{aligned}
\end{align*}
Well-definedness lemmas:
\begin{lemma}[Expression relation uniformity]
\label{lem:stder-dc}
  \begin{align*}
    & \forall \stdvr \ldotp \forall n' \leq n \ldotp \forall W \ldotp \forall \pc \ldotp\\
    & \quad \npair{\pc} \in \stder(\stdvr)(W) \Rightarrow \npair[n']{\pc} \in \stder(\stdvr)(W) 
 \end{align*}
\end{lemma}
\begin{lemma}[Expression relation non-expansive in world]
\label{lem:stder-ne-worlds}
\begin{align*}
  \forall \stdvr \ldotp \forall W_1 \nequal W_2 \ldotp \stder(\stdvr)(W_1) \nequal \stder(\stdvr)(W_2)
\end{align*}
\end{lemma}

@@

\begin{lemma}[Value relation uniformity]
  \begin{align*}
    & \forall V, W, n, n' \ldotp \\
    & \quad n' \leq n \land n \in \stdvr(V)(W) \\
    & \qquad \Rightarrow n' \in \stdvr(V)(W)
  \end{align*}
\end{lemma}

\begin{lemma}[Value relation non-expansive in $V$]
  \begin{align*}
    & \forall V, V', n \ldotp \\
    & \quad V \nequal V' \Rightarrow \stdvr(V) \nequal \stdvr(V')
  \end{align*}
\end{lemma}

\begin{lemma}[Value relation monotone in world]
  \begin{align*}
    & \forall V, W, W' \ldotp \\
    & W' \future W \Rightarrow \stdvr(V)(W') \supseteq \stdvr(V)(W)
  \end{align*} 
\end{lemma}

\begin{lemma}[Value relation non-expansive in world]
  \begin{align*}
    & \forall V, n, W, W' \ldotp \\
    & W \nequal W' \Rightarrow \stdvr(V)(W) \nequal \stdvr(V)(W')
  \end{align*} 
\end{lemma}

\begin{lemma}[Value relation contractive]
  \begin{align*}
    & \forall V, V', n \ldotp \\
    & \quad V \nequal V' \Rightarrow \stdvr(V) \nequal[n+1] \stdvr(V')
  \end{align*}
\end{lemma}

Using the Banach fixed-point theorem, we can find a fixed point for $\stdvr$ We will use this fixed point in the next section to define the logical relation we use in practice.

>>>>

\begin{lemma}[Register relation non-expansive in worlds]
  \label{lem:reg-ne-worlds}
  \begin{align*}
    &\forall \stdvr, n \ldotp \forall W, W' \ldotp \\
    &\quad W \nequal W' \\
    &\qquad \Rightarrow \stdrr(\stdvr)(W) \nequal \stdrr(\stdvr)(W')
  \end{align*}
\end{lemma}

@@

\begin{lemma}[Continuation relation non-expansive in worlds]
  \label{lem:stdkr-ne-worlds}
  \begin{align*}
    &\forall \stdvr, n \ldotp \forall W, W' \ldotp\\
    &\quad W \nequal W' \\
    &\qquad \Rightarrow \stdkr(\stdvr)(W) \nequal \stdkr(\stdvr)(W')
  \end{align*}
\end{lemma}

@@

\subsubsection{Expression Relation}
\label{subsubsection:expression-relation}
The expression relation is defined as follows:
\begin{align*}
  \stder \quad : & \quad  (\Worlds \monnefun \UPred{\Words}) \nefun \Worlds \nefun \UPred{\Words} \\%TODO: Check whether this needs to be monotone
  \stder \defeq & \lambda \stdvr \ldotp \lambda W \ldotp \{ \npair{\pc} \mid 
  \begin{aligned}[t]
    & \forall n' \leq n \ldotp\\
    & \quad \forall \npair[n']{\reg} \in \stdrr(\stdvr)(W) \ldotp \\
    & \quad \quad \forall \npair[n']{c} \in \stdkr(\stdvr)(W) \ldotp \\
    & \quad \qquad  \forall \heapSat[\hs]{n'}{W} \ldotp \\
    & \quad \qquad \quad \npair[n']{(\reg\update{r_0}{c}\update{\pcreg}{\pc},\hs)} \in \observations(W) \}
  \end{aligned}
\end{align*}
Well-definedness lemmas:
\begin{lemma}[Expression relation uniformity]
\label{lem:stder-dc}
  \begin{align*}
    & \forall \stdvr \ldotp \forall n' \leq n \ldotp \forall W \ldotp \forall \pc \ldotp\\
    & \quad \npair{\pc} \in \stder(\stdvr)(W) \Rightarrow \npair[n']{\pc} \in \stder(\stdvr)(W) 
 \end{align*}
\end{lemma}

\begin{lemma}[Expression relation non-expansive in world]
\label{lem:stder-ne-worlds}
\begin{align*}
  & \forall \stdvr \ldotp \forall W_1 \nequal W_2 \ldotp \stder(\stdvr)(W_1) \nequal \stder(\stdvr)(W_2)
\end{align*}
\end{lemma}

@@

\begin{lemma}[Value relation uniformity]
\label{lem:stdvr-dc}
  \begin{align*}
    & \forall V, W, n, n' \ldotp \\
    & \quad n' \leq n \land n \in \stdvr(V)(W) \\
    & \qquad \Rightarrow n' \in \stdvr(V)(W)
  \end{align*}
\end{lemma}

\begin{lemma}[Value relation non-expansive in $V$]
\label{lem:stdvr-ne-V}
  \begin{align*}
    & \forall V, V', n \ldotp \\
    & \quad V \nequal V' \Rightarrow \stdvr(V) \nequal \stdvr(V')
  \end{align*}
\end{lemma}

\begin{lemma}[Value relation monotone in worlds]
\label{lem:stdvr-mono-world}
  \begin{align*}
    & \forall V, W, W' \ldotp \\
    & W' \future W \Rightarrow \stdvr(V)(W') \supseteq \stdvr(V)(W)
  \end{align*} 
\end{lemma}

\begin{lemma}[Value relation non-expansive in worlds]
\label{lem:stdvr-ne-worlds}
  \begin{align*}
    & \forall V, n, W, W' \ldotp \\
    & W \nequal W' \Rightarrow \stdvr(V)(W) \nequal \stdvr(V)(W')
  \end{align*} 
\end{lemma}

\begin{lemma}[Value relation contractive]
\label{lem:stdvr-con}
  \begin{align*}
    & \forall V, V', n \ldotp \\
    & \quad V \nequal V' \Rightarrow \stdvr(V) \nequal[n+1] \stdvr(V')
  \end{align*}
\end{lemma}

Seeing as Lemma~\ref{lem:stdvr-con} gives us that $\stdvr$ is contractive, the Banach fixed-point theorem gives us a fixed-point for $\stdvr$. We will use this fixed point in the next section to define the logical relation we use in practice.
